\documentclass[a4paper,twoside]{tufte-handout}

%% Preamble
\input{preamble}
\input{settings}

\begin{document}

\title[Cosmic Ray Tracker calibration]{%
  \setlength{\parindent}{0pt}%
  {\LARGE
    SiPM Gain calibration \par
    for the scintillating Cosmic Ray Tracker
    \vspace{9cm}

  }
  {\normalsize
    Master thesis \par 
    Faculty of Sciences, University of Bern \par \vspace{3cm}

    Submitted by
  }
}
\author{Pablo Verg\'es}


\date{2016}

\maketitle

{%
  \vspace{6cm}
  \setlength{\parindent}{0pt}%
  Supervisor \\
  \textbf{Prof. Dr. Igor Kreslo}
}

\newpage
\begin{abstract}
  \setlength{\parindent}{0pt}%

  The \gls{sipm}'s gain and its dependency on the bias voltage is studied and used to improve the distribution of gains within a \gls{crt} module. 

  The distribution of gains is displayed before and after calibration.

  Further studies on the \gls{crt} modules with varying power supply and bias voltages are presented.
\end{abstract}
\newpage

% Define acronyms
\input{glossaries}

\tableofcontents
\newpage

\input{ch1intro}
\clearpage
\newpage

\input{ch3detection}
\clearpage
\newpage

\input{ch2interactions}
\clearpage
\newpage

\input{ch4sources}
\clearpage
\newpage

\input{ch5sterile}
\clearpage
\newpage

\input{ch5anomalies}
\clearpage
\newpage

\input{ch6sbnp}
\clearpage
\newpage

\input{ch7cosmogenics}
\clearpage
\newpage

\input{ch8crt}
\clearpage
\newpage

\input{ch8panel}
\clearpage
\newpage

\input{ch8feb}
\clearpage
\pagebreak

\input{ch9calibration}
\clearpage
\pagebreak

\input{ch10experiments}
\clearpage
\newpage

\input{ch11conclusions}
\clearpage
\newpage

%\input{ch12software}
%\cleardoublepage
%\newpage

%\glsaddall
\glossarystyle{list}
\printglossary[type=\acronymtype]
\newpage

%% Bibliography
\bibliographystyle{plainnat}
\bibliography{research}
\newpage

%% Appendices
\begin{appendices}
  \section*{Declaration of consent}

  on the basis of Article 28. para. 2 of the RSL05 phil.-nat.

  \vspace*{12em}
  \begin{table}
  \centering
  \begin{tabular}{ l l }
    \toprule
    Last / First name  & Verg\'es Pablo \\
    Matriculation Nr.  & 04-812-269 \\
    Study program      & Master \\
    Title of thesis    & SiPM Gain calibration \\
                       & for the scintillating Cosmic Ray Tracker \\
    Supervisor         & Prof. Dr. Igor Kreslo \\

    \bottomrule
  \end{tabular}
  \end{table}
  \vspace*{12em}
  I declare herewith that this thesis is my own work and that I have not used any sources other than those stated.
  I have indicated the adoption of quotations as well as thoughts taken from other authors as such in the thesis.
  I am aware that the Senate pursuant to Article 36 para. 1 lit. r of the University Act of 5 September, 1996 is authorised to revoke the title awarded on the basis of this thesis.
  I allow herewith inspection in this thesis

  \vspace*{12em}
  \begin{table}
  \begin{tabular}{ l l }
    Place / Date  & \hspace*{20em} \\
    \\
    \\
    \hspace*{20em} & Signature \\
  \end{tabular}
  \end{table}
\end{appendices}

\end{document}
